\plaintitle

### 2018-04-03 paper/paper.tex
...

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref} なんかわからない
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{``\texttt{#1}''}

@@

@@

>>>>

% Load basic packages
\usepackage{balance}       % to better equalize the last page
% \usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage{graphicx}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref} なんかわからない
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{``\texttt{#1}''}
\long\def\sf#1{``\textsf{#1}''}

@@

Help documents used in ExpandHelp are provided as a set of data entries
consisting of a regular expression which represents the help entry description
and a corresponding command pattern.
A description string is used to produce natural language texts
which are easily understandable to users,
while command patterns are used for invoking commands or calling library functions
corresponding to the description.
%
For example, a help entry for finding a restaurant on the Web consists of
the following data:

\begin{quote}
  description: \\
  \texttt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
  command: \\
  \texttt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\sf{Find a Chinese restaurant in San Francisco}, 
\sf{Find a Chinese restaurant in Chicago}, etc.,
and the second part, command part,
is used to generate a command for accessing \texttt{Yelp.com}.
% Here, $1 and $2 corresponds to the matched pattern in the regular expression.
In the first example, \sf{Chinese} and \sf{San Francisco}
match the first and second parentheses of the regular expression, and
these values are assigned to \texttt{\$1} and \texttt{\$2}
for the command part, generating a URL
\texttt{http://www.yelp. com/search?find\_loc=San\%20Francisco\&find\_desc= Chinese}.

When the matched pattern like \sf{San Francisco}
cannot be directly used in the command,
parameters for the command can be put after the description string,
separated by a TAB character.
For example, when a number like ``\texttt{29247}'' should be used
for checking the
weather of San Francisco, we can describe the help entry like this:

\begin{quote}\small
 description: \\
 \texttt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
 command: \\
 \texttt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
\end{quote}

Here, selecting a menu entry \sf{Check the weather of San Francisco}
will produce a command
\texttt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.

-----------------------------------

@@

\subsection*{Generating help menu entries}

Finding appropriate entries from the huge help document space is performed in two steps.
First, we parse the regular expression to
generate a state transition diagram which represents all the strings represented
in the regular expression.
Second, we generate all the description strings by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.
% and we will describe the details of the algorithm later in this section.

\subsection*{Phase 1: Generating a state transition diagram from a regular expression}

Regular expressions are widely used for finding a pattern in a text string
in modern programming languages and in the Unix environment.
In ExpandHelp, we use a regular expression for
generating various patterns of descriptions in a short form.
For example, we use a short regular expression
\tt{(remove|delete|erase) (data|file)}
for representing expressions like
\sf{remove data},
\sf{erase file},
etc.

Converting a regular expression to a state transition machine is a straightforward task.
When we have a regular expression
\tt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
we can parse the string and convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
\caption{State transition diagram for finding a restaurant.}
\label{statemachine1}
\end{figure}

% \includegraphics[height=12pt]{figures/startnode.pdf}
% depicts the start node.

By traversing the nodes and links in this state machine,
we can generate the following description texts.

\begin{quote}
\small
\textsf{Find a Chinese restaurant in San Francisco} \\
\textsf{Find a Chinese restaurant in Chicago} \\
...\\
\textsf{Find a Vietnamese restaurant in New York}\\
\end{quote}

\subsection*{Phase 2: Generating texts from a state transition diagram}

Using the state transition diagram shown in Figure \ref{statemachine1},
ExpandHelp generates all the strings represented in the regular expressions,
and filter them by the pattern provided by the user.

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node (\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node \raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
the system generates a string \sf{Find a} and proceeds to the next node.
In the second generation,
the system can add \sf{Chinese}, \sf{Korean}, and \sf{Vietnamese}
to \sf{Find a}, generating
\sf{Find a Chinese},
\sf{Find a Korean}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\texttt{(0|1)+}'' which represents infinite length of
strings consisting of \texttt{0}s and \texttt{1}s, so the generation should be
terminated at certain generation.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
\caption{Generating a text tree from a state transition machine.}
\label{gentree1}
\end{figure}

\subsection{Generate-and-Filter}

Generating all the texts in this way before finding matched strings is
inefficient, because the amount of generated texts can easily become huge.
Instead, the system performs the patter matching as soon as a text is generated,
for saving time and memory.

``Generate-and-test\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}''
technique is a simple and effective strategy
used for solving puzzles and AI problems.
Using this strategy, the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

To solve this problem,
controlling the generation part from the testing part is usually effective.
In the 8-Queen problem,
whenever the testing part finds two queens in the same row or column,
it can tell the generation part to
give up current layout in the early stage and proceed to the next layout.

Similarly in our case,
it is not efficient to perform the matching operation
after generating all the texts from the regular expression,
and it is better to calculate the matching
at the time of generating each text.
We call it the ``\textit{generate-and-filter}'' strategy,
and implemented the algorithm in ExpandHelp.
Unlike simple puzzle problems where
conditions are strict and finding one solution is enough,
our goal is to find help description strings which
fits the query pattern while allowing errors.
For this goal,
the system should perform approximate pattern matching
without sacrificing processing speed.
%
We could implement flexible generate-and-filter by using a simple and efficient
approximate pattern matching algorithm based on the ``shifter algorithm''.
